Normalization by Evaluation for Sized Dependent Types

### 2018-03-02 nbe/icfp17.tex
ICFP17: fixed proof of core lemma

\nextcase $T \evalsto \forallT B$ with $B[\alpha] \in \SET[\ell] \mforall \alpha \in \SIZE$
\begin{gather*}
%   \ru{B[\alpha] \in \SET[\ell] \mforall \alpha \in \SIZE
%     }{T \in \SET[\ell]}
% \\[2ex]
  \ru{S_1 \evalsto \forallT{B_1} \qquad
      B[\alpha] \shape B_1[\alpha'] \mforall \alpha, \alpha' \in \SIZE
    }{T \shape S_1}
\\[1.5ex]
  \ru{S_2 \evalsto \forallT{B_2} \qquad
      B[\alpha] \shape B_2[\alpha'] \mforall \alpha, \alpha' \in \SIZE
    }{T \shape S_2}
\end{gather*}
\begin{enumerate}
\item To show $\up{S_1}{n_1} = \up{S_2}{n_2} \in T$ assume arbitrary $\alpha_1,\alpha_2 \in \SIZE$.
  Since $n_1 \ann{\alpha_1} = n_2 \ann{\alpha_2} \in \NE$ by Lemma~\ref{lem:closne}, we obtain
  $\up{B_1[\alpha_1]}{(n_1 \ann{\alpha_1})} = \up{B_2[\alpha_2]}{(n_2 \ann{\alpha_2})} \in B[\alpha_1]$
  by induction hypothesis.
  Thus, $(\up{S_1}{n_1}) \ann{\alpha_1} = (\up{S_2}{n_2}) \ann{\alpha_2} \in B[\alpha_1]$
  by weak head expansion, which entails the goal by definition of $\EL(T)$.
\item Assume $k \in \NN$ and note that $\lev k = \lev k \in \SIZE$, hence,
  $t_1\,\ann{\lev k} = t_2\,\ann{\lev k} \in B[\lev k]$.  Thus, by induction hypothesis,
  $\R{k+1}{\down{B_i[\lev k]}(t_i\,\ann{\lev k})}{v_i}$ with $v_1 \nfeq v_2$, and finally
  $\R k {\down{S_i} t_i} {\lambda v_i}$ by definition of read back.
\qed
\end{enumerate}

>>>>

\nextcase $T \evalsto \forallT B$ with $B[\alpha] \in \SET[\ell] \mforall \alpha \in \SIZE$
\begin{gather*}
%   \ru{B[\alpha] \in \SET[\ell] \mforall \alpha \in \SIZE
%     }{T \in \SET[\ell]}
% \\[2ex]
  \ru{S_1 \evalsto \forallT{B_1} \qquad
      B[\alpha] \shape B_1[\alpha'] \mforall \alpha, \alpha' \in \SIZE
    }{T \shape S_1}
\\[1.5ex]
  \ru{S_2 \evalsto \forallT{B_2} \qquad
      B[\alpha] \shape B_2[\alpha'] \mforall \alpha, \alpha' \in \SIZE
    }{T \shape S_2}
\end{gather*}
\begin{enumerate}
\item To show $\up{S_1}{n_1} = \up{S_2}{n_2} \in T$ assume arbitrary $\alpha_1,\alpha_2,\beta \in \SIZE$.
  Since $n_1 \ann{\alpha_1} = n_2 \ann{\alpha_2} \in \NE$ by Lemma~\ref{lem:closne}, we obtain
  $\up{B_1[\alpha_1]}{(n_1 \ann{\alpha_1})} = \up{B_2[\alpha_2]}{(n_2 \ann{\alpha_2})} \in B[\beta]$
  by induction hypothesis.
  Thus, $(\up{S_1}{n_1}) \ann{\alpha_1} = (\up{S_2}{n_2}) \ann{\alpha_2} \in B[\beta]$
  by weak head expansion, which entails the goal by definition of $\EL(T)$.
\item Assume $k \in \NN$ and note that $\lev k = \lev k \in \SIZE$, hence,
  $t_1\,\ann{\lev k} = t_2\,\ann{\lev k} \in B[\lev k]$.  Thus, by induction hypothesis,
  $\R{k+1}{\down{B_i[\lev k]}(t_i\,\ann{\lev k})}{v_i}$ with $v_1 \nfeq v_2$, and finally
  $\R k {\down{S_i} t_i} {\lambda v_i}$ by definition of read back.
\qed
\end{enumerate}
